The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-21 paper.tex
update

  \Cref{fig__numberDensityHistogram} plots the volume filling factor as a function of\
  initial number density within the disc without jet source.\

  \Cref{fig__zoom-in-disc} shows a close-up view of the\
  pressure, temperature, and number density slices
  in the y-z plane through the center of the disc.

>>>>

  In this way, we plot the volume filling factor as a function of\
  initial number density within the disc without the jet source in \Cref{fig__numberDensityHistogram},\
  and show a close-up view of the\
  pressure, temperature, and number density slices
  in the y-z plane through the center of the disc in \Cref{fig__zoom-in-disc} .
